\textbf{ Matching the forecast horizon with the relevant ecological processes }

### 2019-10-16 doc/manuscript.tex
Format changes for EcoLetts

\author[1]{Peter B. Adler}  %\thanks{Corresponding author. Department of Wildland Resources and the Ecology Center, Utah State University, Logan, Utah Email: peter.adler@usu.edu}}
\author[2,3,4]{Ethan P. White}
\author[5]{Michael H. Cortez}
\affil[1]{Department of Wildland Resources and the Ecology Center, Utah State University, Logan, Utah}
\affil[2]{Department of Wildlife Ecology and Conservation, University of Florida, Gainesville, Florida}
\affil[3]{Informatics Institute, University of Florida, Gainesville, Florida}
\affil[4]{Biodiversity Institute, University of Florida, Gainesville, Florida}
\affil[5]{Department of Biological Science, Florida State University, Tallahasee, Florida}

@@

@@

\vspace{0.2in}

\textbf{\large{Keywords:}} dispersal, ecological forecasting, eco-evolutionary dynamics, global change, selection

@@

>>>>

\author[1]{Peter B. Adler}  
\author[2,3,4]{Ethan P. White}
\author[5]{Michael H. Cortez}
\affil[1]{Department of Wildland Resources and the Ecology Center, Utah State University, Logan, Utah}
\affil[2]{Department of Wildlife Ecology and Conservation, University of Florida, Gainesville, Florida}
\affil[3]{Informatics Institute, University of Florida, Gainesville, Florida}
\affil[4]{Biodiversity Institute, University of Florida, Gainesville, Florida}
\affil[5]{Department of Biological Science, Florida State University, Tallahasee, Florida}

@@

% rest of title page
\noindent \emph{Statement of authorship:} PBA and EPW designed the study, PBA and MHC built the models, and PBA analyzed the models. PBA wrote the first draft of the manuscript, and all authors contributed substantially to revisions.

\noindent \emph{Data accessibility statement:} The manuscript contains no original data. All computer code is available at https://github.com/pbadler/space-time-forecast. Upon acceptance of the manuscript, code will be archived at Zenodo.

\noindent \emph{Running title:} Forecast horizon and ecological process

\noindent \emph{Keywords:} dispersal, ecological forecasting, eco-evolutionary dynamics, global change, selection

\noindent \emph{Word counts:} 174 words in abstract; 4044 words in main text.

\noindent \emph{References}: 35

\noindent \emph{References}: 6 figures, no tables or text boxes

\noindent \emph{Corresponding author:} Peter Adler, Department of Wildland Resources and the Ecology Center, Utah State University, Logan, Utah, 84322, USA; email: peter.adler@usu.edu; tel: 435-797-1021

@@

@@

\clearpage

\clearpage

\clearpage

\clearpage

\clearpage
